A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.

### 2015-03-10 paper/methodology.tex
Methodology: Dust attenuation

%Dust Extinction
\subsection{MCMC}
We used a Markov Chain Monte Carlo method to find the best parameters and its 
uncertainties over each one of the boxes and each observational dataset.

>>>>

\subsection{Dust Attenuation}

Dust in galaxies absorbs part of the UV radiation and reemits on IR. The more massive is the galaxy
then more dust contains and dust attenuation will be bigger.

The UV Spectral Slope $\beta$ was introduced by \citet{meurer99} as a color index to 
study dust attenuation in high redshift galaxies calibrating with local galaxies. 
This index is becomes from a power law
fitting, with the flux $f$ as function of the wavelength $\lambda$,
\[ f \propto \lambda^\beta\],
The relation they found is:
\begin{equation}
A = 4.43 + 1.99 \beta
\end{equation}.

\citet{bouwens12b} found a linear relation between $\beta$ and the UV magnitude.
\begin{equation}
\langle \beta \rangle = \frac{d \beta}{d M_{UV}} \left( M_{UV,AB}+19.5 \right) + \beta_{M_{UV}=-19.5}
\end{equation}

We use a similar dust attenuation model as the used by \cite{smit12} with 
$ \beta_{M_{UV}=-19.5} = -2.20$ and $d \beta/d M_{UV} = -0.21$ at $z=5.9$ 
according \citep(bouwens12b), imposing also the condition:
\[ A \geq 0 \]

\subsection{MCMC}
We used a Markov Chain Monte Carlo method to find the best parameters and its 
uncertainties over each one of the boxes and each observational dataset.
